Rough calculations

### 2015-10-30 notes/rough-calculations.Rmd
notes

---
title: "Clines from PDE"
date: "`r date()`"
---

@@

>>>>

---
title: "Rough calculations"
date: "`r date()`"
---

@@

6.  For a pair of sites, what is the correlation in ancestral state at those loci,
    given the state at the selected locus
    (and, also, averaged over choice of selected locus).

    a.  Allow for ascertainment of SNPs in extremal individuals
        by estimating probability of coalescence in ancestral populations
        from the extremal individuals.
        For each pair of loci, correlation of these two loci with extremal individuals.

How a neutral cline flattens
============================

1.  *What is the width of the cline at a linked, neutral locus?*
    *How long does it take to flatten out?*
    *How far from the cline do you have to go to find mostly one type?*
